---
title: "0912"
author: "Yiyao Zhou"
date: "9/12/2018"
output: html_document
---
```{r}
library(forecast)
library(ggplot2)
```

# FRED
Macro data: https://fred.stlouisfed.org/

Real number GDP: https://fred.stlouisfed.org/series/GDPC1
Unemployment: https://fred.stlouisfed.org/series/UNRATE

# Estimateing a CAPM
```{r}
setwd("/Users/yiyao/Desktop/ECON-FIN-250A-1-Forecasting-in-Finance-and-Economics/ECON-FIN-250A-1-Forecasting-in-Finance-and-Economics")
ibmmkt <- read.csv("ibmcrsp.csv")
head(ibmmkt)

# create time series
ibmts <- ts(ibmmkt$RET,start=c(1926,1),freq=12)
vwts <-  ts(ibmmkt$vwretd,start=c(1926,1),freq=12)
tbts   <-  ts(ibmmkt$t90ret,start=c(1926,1),freq=12)

# replace missing returns with 0 (hopefully not too many)
ibmts[ is.na(ibmts) ] <- 0 

#calculate excess returns
# ibmts: IBM retruns
# tbts: T-bill returns (risk-free return)
# vwts: Market returns
ibmex <- ibmts - tbts
vwex  <- vwts - tbts

# estimate IBM beta
# lm is basic linear model in R
# Note model notation
# to get info type summary(capm.mod)
capm.mod <- lm(ibmex ~ vwex)
summary(capm.mod)
```

anscombe example: same regression model, different dataset
plot
```{r}
example('anscombe')
```

# Logan Passenger example
Data Source: https://www.transtats.bts.gov/Data_Elements.aspx?Data=1
```{r}
# Passengers (All Carriers - Boston, MA: Logan International (Origin Airport))  
# (www.bts.dot.gov)
logan.data <- read.csv("LoganPassengers.csv")
# data comes as monthly entries with annual totals (see website)
# need to remove annual values (these are just much bigger than monthly)
# set 
logan.data <- logan.data[logan.data$total < 5000000,]
logan.ts <- ts(logan.data$total,start = c(2002,10), freq = 12)
plot(logan.ts,xlab = "Year",ylab = "Passengers",bty = "l")
grid()
# if you want to try ggplot2
# my favorite basic would be
# p <- autoplot(logan.ts)
# p <- autoplot(logan.ts)+theme_light(base_size=16)
# print(p)
```
Short series
Weak seasonality
Trend: sort of, linear??

Zooming in and windows
```{r}
# Display subwindow of data set
# Load airport passenger data
logan.data <- read.csv("LoganPassengers.csv")
logan.data <- logan.data[logan.data$total<5000000,]
logan.ts <- ts(logan.data$total,start=c(2002,10), freq=12)
# create subwindow (3 years)
logan.ts.zoom <- window(logan.ts,start=c(2002,10),end=c(2005,12))
# plot it
plot(logan.ts.zoom,xlab="Year",ylab="Passengers",bty="l")
grid()
```
Get a very detailed picture of the early years
Complicated season patern:low in Jan and fall, high in summer time (June) and holiday season (Dec)

# U.S. Gasoline Supply
```{r}
# US product supplied of finished motor gasoline
# Source U.S. Energy Information Administration
gas.data <- read.csv("gasoline.csv")
gas.ts <- ts(gas.data$gasoline,start = c(1945,1),freq = 12)
plot(gas.ts)
grid()
```
US product supplied of finished motor gasoline (monthly)
Source: Energy Information Administration
Longer series
Strong seasonality
Changing trends: like 1980 went down, then went up...

# Dow Jones Industrials
```{r}

``